The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-09-06 article.tex
Duplicated closely

On the other hand, for many modules, the test code is now more closely closely
linked to the code being tested: both reside in the same folder, though we
adhere to the Maven custom to have src/main/java and a src/test/java folders.
For a few modules, however, this solution introduces circular dependencies, in
which case a separate Maven module is created for the tests.

>>>>

On the other hand, for many modules, the test code is now more closely
linked to the code being tested: both reside in the same folder, though we
adhere to the Maven custom to have src/main/java and a src/test/java folders.
For a few modules, however, this solution introduces circular dependencies, in
which case a separate Maven module is created for the tests.
